Automatic Differentiation Accelerates Inference for Partially Observed Markov Processes

### 2024-08-20 paper/appendix/coverletter.tex
Updates from Overleaf

Please consider our manuscript, "Accelerated Inference for Partially Observed Markov Processes using Automatic Differentiation", for publication in PNAS.

>>>>

Please consider our manuscript, ``Automatic Differentiation Accelerates Inference for Partially Observed Markov Processes", for publication in PNAS.
